---
title: "Data Chek ver3 last biz day version"
output:
  html_document:
    df_print: paged
---


This is to use IvyDB pricedata and another factor DB to tou ji dao ba. This file is to check the basic data integrity. It is reading from the root directory for the simplicity now.

Now I am buring the previous data prep step so we will have fewer ouputs we will just check the graphs for each factor
```{r include=FALSE}
library(xts)
# library(h2o)
require(PerformanceAnalytics)
require(quantmod)
library(lubridate)
library(data.table)
library(tidyverse)
library(tibbletime)


```

### **_Step.1 Read IVYDB mapping and ZY DB to inner_join on cusip._**
 

```{r include=FALSE}

mapping=readRDS("securitylist.rds") # the IVYDB mapping
IVYmapping<-mapping %>%
  select(SecurityID,CUSIP,Ticker) 

print(head(IVYmapping))

ZYmapping=read.csv("cusip.csv",stringsAsFactors = F, header = F) #ZY's mapping, no header, will add by myself.

ZYmapping<-ZYmapping %>% 
  rename(Date=V1,BBG=V2,CUSIP=V5,Name=V6) %>%  
  select(Date,BBG,CUSIP,Name) # rename the columns, and only keep those columns
print(head(ZYmapping))

```



```{r include=FALSE}
mess=paste("ZY DB # of stocks",nrow(ZYmapping))
print(mess)

mess=paste("IVY DB # of stocks",nrow(IVYmapping))
print(mess)

ZYmapping<-ZYmapping %>% 
  mutate(CUSIP=str_sub(CUSIP,start=1,end=-2)) # remove the last digit

finalmapping<-IVYmapping %>% 
  inner_join(ZYmapping,by="CUSIP")

mess=paste("megedDB # of stocks",nrow(finalmapping))
print(mess)

missingID=ZYmapping %>% 
  filter(!CUSIP %in% finalmapping$CUSIP)

print(missingID)

# Something fucking weird is that GE's cusip is 36960430 in IVY? STX is G7997R10
```



```{r include=FALSE}
IVYmapping2<-IVYmapping %>% 
  mutate(CUSIP=ifelse(CUSIP=="36960430","36960410",CUSIP)) %>% 
  mutate(CUSIP=ifelse(CUSIP=="57387410","G5876H10",CUSIP)) %>%
  mutate(CUSIP=ifelse(CUSIP=="G7997R10","G7945M10",CUSIP)) %>%
  mutate(CUSIP=ifelse(CUSIP=="44891N20","44891N10",CUSIP)) %>%
  mutate(CUSIP=ifelse(CUSIP=="55024110","15670010",CUSIP)) 

finalmapping<-IVYmapping2 %>% 
  inner_join(ZYmapping,by="CUSIP") %>%
  mutate(Date=as.Date(Date)) %>% 
  select(-Date) # remove the Date column for nowm, may need it later on for point in time study

mess=paste("megedDB # of stocks",nrow(finalmapping))
print(mess)

print(head(finalmapping))
```

### **_Step.2 Check All the factors_**
(1) Get the all factor file。
```{r}

# get all the factors
factors<-fread("ss.csv")

colnames(factors)=c("Date","CUSIP","Factor","Value")
factors<-factors %>% 
  mutate(Date=as.Date(Date),Y=year(Date),M=month(Date)) %>% 
  mutate(CUSIP=str_sub(CUSIP,start=1,end=-2)) # CUSIP treatment

print(head(factors))
```
(2) Get the IVYDB price data and inner_join with the mapping info at first. Check old rmd file for explanations.

```{r}
# using feather data now. Can switch to fst for faster data load if working with R only
pricedata<-rio::import("JQCpricedata.feather")
print(head(pricedata))

newpricedata<-pricedata %>% 
  inner_join(finalmapping,by="SecurityID") # about 1/10 of the all stock data, make sense ha
print(head(newpricedata))
```

(3) Combine with each factor info. 看起来所有因子都对齐到了月末 所以可以用一个简单的办法change the factor df to wide format with each col being a single factor (这个要取决与数据格式 以后不一定这样合适哈)
<1> Inner_join style on Date. 
```{r}
# expand factors to wide format
factors_w<-factors %>% 
  pivot_wider(names_from = Factor,values_from = Value) # default is fill NA for missing factors

## 现在看会有很多NA 所以后面算ML或者因子收益要多注意了， 这么多NA对ML有很多挑战 我之前也没有搞过这么多NA的，要我们一起
#看这些NA的来的原因和是否可以fillna from prev non-na
print(factors_w)


```
Now we can combine the factors with the price data
```{r}
final<-newpricedata %>% 
  select(Date,SecurityID,CUSIP,BBG,size_rank,Price,Cumret,tempSPX) %>% 
  inner_join(factors_w,by=c("CUSIP","Date"))


```

(4) Use the factors to evaluate the factor performance.In my codes "y" is the return for the next period. We will use decile rank for now and we can use Z-score weighted neutral style.
```{r}
factordata<-final %>%
  group_by(SecurityID) %>% 
  arrange(Date) %>% 
  mutate(y=lead(Cumret)/Cumret)  # you cannot do na.omit at this stage as you have so many NAs for factor columns

divs=10 # deciles.

factornames=colnames(factordata)[11:(ncol(factordata)-1)]
nfactors=length(factornames)

for (i in 1:nfactors)
{
  var=factornames[i]
  factorret<-factordata %>% 
  group_by(M,Y) %>% 
  mutate(decile=ntile(get(var),divs)) %>% 
  group_by(M,Y,decile) %>%
  summarise(decileret=mean(y,na.rm=T)-1,Date=min(Date))

p1<-factorret %>%
    group_by(decile) %>%
    summarise(Decileret=mean(decileret,na.rm=T)) %>%
    ggplot(aes(x=decile,y=Decileret)) + geom_bar(stat = "identity") + ggtitle(var)
print(p1)
  
LSret<-factorret %>% 
  group_by(M,Y) %>% 
  arrange(decile) %>% 
  mutate(weight = case_when(
      decile==10 ~ 1,
      decile==1 ~ -1,
      TRUE     ~ 0
    ))

strat=LSret %>% 
  group_by(Date) %>% 
  summarise(portret=mean(weight*decileret))

strats=xts(strat$portret,order.by = strat$Date)
source("C:/jiaqifiles/R code/Persupportfunc.r")
mess=(var)
PnLreport(strats,info = mess,freq=12)
}


```

